---
title: "ENVS 193DS Workshop 7"
date: 2024-05-15
author: "Jackie Chen"
format: html
---

# Set up

First, make sure your name is in the `author:` field at the top of this document.  

Second, install the following packages (remember to do this in your Console):  

- `here`: read about it at [this link](https://here.r-lib.org/)  
- `ggeffects`: read about it at [this link](https://strengejacke.github.io/ggeffects/)

Third, read in your packages and data.

```{r packages-and-data}
library(tidyverse) # general use
library(here) # file organization
library(ggeffects) # model predictions
library(flextable) # creating tables

abalone <- read_csv(here("data", "abalone_growth.csv"))
```

Look at the file structure in this repository.  

Where is this `.qmd` file? Where is the `abalone_growth.csv` file?  

The `.qmd` file is in the code folder, while the `abalone_growth.csv` file is in the data folder.

Note the file path within the `read_csv()` function. How is this different from how we've stored and read data before?

This is different from how we stored and read data before by that here() was used instead of providing the file path to store and read data. 

**COMMIT AND PUSH YOUR CHANGES!**

# 1. Look at your data.

Look at your data. Here's three different ways of looking at your data:

```{r using-str}
str(abalone)
```

```{r using-glimpse}
glimpse(abalone)
```

```{r using-class}
class(abalone)
```

Compare the three ways of looking at data below. What's different about the outputs, and what's similar?  

All of the three ways provide information about the data. While str and glimpse provide several values of temperature and data, class does not. Moreover, str has temperature and growth as num [1:27] but specifies these attributes afterwards as temperature = col_double() and growth = col_double(), while glimpse directly specifies temperature and growth as dbl (double).

**COMMIT AND PUSH YOUR CHANGES!**

Then, visualize your data.  

Annotate the code to make `abalone_plot`. Make the plot look better by:  

1. changing the size of the points so that they're larger and easier to see  
2. making the background of the panel white with no gridlines  

```{r prelim-data-visualization}
abalone_plot <- ggplot(data = abalone,
                       aes(x = temperature,
                           y = growth)) +
  geom_point() +
  theme(# getting rid of gridlines
    panel.grid = element_blank()
  )

abalone_plot
```

**COMMIT AND PUSH YOUR CHANGES!**

# 2. Write out your model.

Write your model in words:  

_model in words here_  

Annotate the code to create the model object `abalone_model`.

```{r abalone-model}
# create model object `abalone_model` using growth and temperature variables
abalone_model <- lm(growth ~ temperature,
                    data = abalone) # use abalone as data for model
```

**COMMIT AND PUSH YOUR CHANGES!**

# 3. Look at the diagnostic plots.

Look at the four diagnostic plots for this model. Annotate the code.

```{r abalone-model-diagnostics}
# check for outliers and normality with the four diagnostic plots
par(mfrow = c(2, 2))
plot(abalone_model)
```

**Note:** Sometimes it is hard to see diagnostics in a small window. Open up a larger version of the plot by clicking "Zoom" in the "Plots" tab in the lower right.

# 4. Look at the model coefficients.

Use `summary()` to look at the model coefficients (slope and intercept) and standard error (precision of the coefficient).

```{r abalone-model-summary}
summary(abalone_model)
```

Make a note of the y-intercept and slope estimates below with the standard error. Round the estimate and standard error to two decimal places.    

_Slope: -0.70 ± 0.05_
_y-intercept: 16.41 ± 0.70_

**COMMIT AND PUSH YOUR CHANGES!**

# 5. Visualize the model predictions.

Get the model predictions using `ggeffect::ggpredict()`.  

Annotate the code below.

```{r abalone-model-predictions}
# get model predictions for abalone growth in abalone_model
model_preds <- ggpredict(abalone_model,
                         terms = "temperature")
```

Look at the `model_preds` object in two ways: using `View(model_preds)` in your console and by displaying the output just running `model_preds`. 

Compare the two outputs. How are they different?  

The outputs are different by that View(model_preds) has the output in a tab and having more columns for model_preds, while displaying the output just running `model_preds` has the output in the console for values of temperature, predicted, and the 95% CI (using the lower and upper bounds of the confidence interval). Unlike View(model_preds), the lower and upper bounds of the 95% CI when running `model_preds` are not in separate columns.

**Note:** you can rename columns in your object from `ggpredict()` to make the data frame easier to work with. For example, you can change `x` to whatever your `x` variable is (in this case, `temperature`), and `predicted` to whatever your `y` variable is (in this case, `growth`). If you do this, you'll have to modify the code below to run.  

**COMMIT AND PUSH YOUR CHANGES!**

Then, plot the data with the model predictions. Annotate the code below. Change the plot by:  

1. changing the size of the points so that they're larger and easier to see  
2. changing the shape of the points to be open circles so that attention is drawn to the model prediction line  
3. changing the color of the points to be different from the line  
4. making the background of the panel white with no gridlines  

```{r abalone-model-plot}
abalone_model_plot <- ggplot(data = abalone,
                             aes(x = temperature,
                                 y = growth)) +
  geom_point() +
  geom_ribbon(data = model_preds,
              aes(x = x,
                  y = predicted,
                  ymin = conf.low,
                  ymax = conf.high),
              alpha = 0.2) +
  geom_line(data = model_preds,
            aes(x = x,
                y = predicted),
            linewidth = 1) +
  theme(# getting rid of gridlines
    panel.grid = element_blank()
  )

abalone_model_plot
```

Create a new folder in this repository called `images`.  

Use `ggsave()` to save `abalone_model_plot` as a .jpg in `images`.  

Annotate the code below.

```{r abalone-plot-save}
ggsave(filename = here("images", "abalone_model_plot.jpg"),
       width = 10,
       height = 8,
       units = "cm")
```


**COMMIT AND PUSH YOUR CHANGES!**

Then, calculate the correlation between temperature and growth.  

```{r abalone-correlation-test}
cor.test(abalone$temperature, abalone$growth,
         method = "pearson")
```

# 6. Describe your model.

Using your notes, write 2-4 sentences about the model results. Start with a broad overarching result (model significance and correlation), then describe specifics of the model estimates (slope and coefficient if relevant), and model predictions (at a specific predictor value, the model predicts _____ response value).  

_write about your model here_ 

**COMMIT AND PUSH YOUR CHANGES!**  

# 7. Render your document and set up GitHub Pages for this repository.

See the [Git/GitHub resource](https://spring-2024.envs-193ds.com/resources/using-github#using-github-pages-to-display-rendered-.html-output) to set up GitHub Pages.  

Find the url for your rendered .html document. Make sure it looks like `yourgithubusername.github.io/repo/filepath/filename.html`. Enter it below.  

jackiechen24.github.io/personal-copy_week-07/code/workshop-07_TEMPLATE_2024-05-15.html

**COMMIT AND PUSH YOUR CHANGES!**  

# 8. Write an informative README.

Read the [README resource](https://spring-2024.envs-193ds.com/resources/writing-a-readme) (also on Canvas for reference).  

Find the `README` in this repository in RStudio.

Write sections for: "General information", "Data and file overview", and "Rendered output".    

In your "Rendered output" section, include the link to the rendered .html document as a hyperlink.  

**COMMIT AND PUSH YOUR CHANGES!**  

